---
title: "p8105_hw5_kz2334"
author: "Kangkang Zhang"
date: "11/7/2018"
output: github_document
---

##Problem 1

Load required packages.

```{r library, message = FALSE}
#load packages
library(tidyverse)
library(viridis)
```
<br>
Import file names to create a dataframe.

```{r import}
file_name = tibble(
  id = list.files("./data/")
)
```
<br>
Read in data for each subject.

```{r import data, message = FALSE}
study_data = file_name %>% 
  mutate(infor = purrr::map(str_c("./data/", id), read_csv)) 

study_data
```
<br>
Tidy the result and manipulate file names to include control arm and subject ID.

```{r tidy}
study_data = study_data %>%
  mutate( id = str_replace(id, ".csv", "")) %>% 
  separate(id, into = c("arm", "id"), sep = "_") %>%
  unnest() %>% 
  gather(week, value = value, week_1:week_8) %>% 
  mutate(week = as.numeric(str_replace(week, "week_", "")))

study_data
```
<br>
Make a spaghetti plot showing observations on each subject over time.
```{r spaghetti plot, fig.align = 'center'}
study_data %>%  
  ggplot(aes(x = week, y = value, color = id, linetype = arm)) + 
  geom_line() +
  labs(
    title = "Spaghetti plot",
    x = "Week",
    y = "Observation"
  ) +
  theme_bw() +
  scale_x_discrete(breaks=seq(0, 8, 1)) +
  scale_linetype_discrete(label = c("Control", "Experimental")) +
  scale_color_viridis(discrete = TRUE)
```

Globally, experimental group has larger observation values than control group. In experimental group, observations increased as time went by. In control group, observations fluctuated within an interval as time went by.

##Problem 2

Import and describe the raw data. 
```{r 2.1 import, message = FALSE} 
homicide_data = read_csv("./p2_data/homicide-data.csv")

homicide_data
```

This dataset contains `r nrow(homicide_data)` rows and `r ncol(homicide_data)` columns, with each row resprenting a single homicide record over the past decade in 50 of the largest American cities. Variables include record ID, reported date, victim's name, victim's race, victim's age, victim's sex, city and state, homicide location, and disposition. 
<br>

---

Create a `city_state` variable and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.
```{r summarise number}
homicide_data = homicide_data %>% 
  mutate(city_state = str_c(city, ", ", state)) 

prop_data = homicide_data %>%
  group_by(city_state) %>% 
  summarise(num_homicide = n(),
            num_unsolved_homi = sum(disposition %in% c("Closed without arrest", "Open/No arrest"))) %>% 
  arrange(desc(num_homicide))

prop_data
```
We can see from the chart that Chicago is the city with the largest number of homicides, 5535.
<br>

For the city of Baltimore, MD, estimate the proportion of homicides that are unsolved; pull the estimated proportion and confidence intervals from the resulting tidy dataframe.
```{r, Baltimore_data}
Baltimore_data = prop_data %>%
  filter(city_state == "Baltimore, MD") 

#proportion test  
result = prop.test(Baltimore_data$num_unsolved_homi, Baltimore_data$num_homicide)

#pull estimated proportion
broom::tidy(result) %>% 
  pull(estimate)

#pull lower side of CI
broom::tidy(result) %>% 
  pull(conf.low)

#pull upper side of CI
broom::tidy(result) %>% 
  pull(conf.high)
```

The estimated proportion is `r broom::tidy(result) %>% pull(estimate)`, 95% confidence interval is (`r broom::tidy(result) %>% pull(conf.low)`, `r broom::tidy(result) %>% pull(conf.high)`).
<br>

---

Run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. 

```{r map, message = FALSE, warning = FALSE}
#map function and create tidy dataframe
prop_data = prop_data %>%
 mutate(results = map2(num_unsolved_homi, num_homicide, prop.test),
        results = map(results, broom::tidy)) %>% 
 unnest() %>% 
 select(city_state, num_homicide, num_unsolved_homi, estimate, conf.low, conf.high)

prop_data
```
<br>
Create a plot that shows the estimates and CIs for each city. Organize cities according to the proportion of unsolved homicides.

```{r plot, fig.align = 'center'}
prop_data %>% 
  mutate(unsolved_prop = num_unsolved_homi/num_homicide,
    city_state = fct_reorder(city_state, unsolved_prop)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Estimate proportion of unsolved homicides for each city",
    x = "City",
    y = "Estimate proportion"
  ) 
```

From the plot we can see that Chicago has the largest esitmate and narrowest CI of proportion of unsolved homicides. We notice that there is abnormal CI for Tulsa, AL. It turns out that the number of homicides and the number of unsolved homicides in Tulsa is 1 and 0. The size is too small, resulting in bias in chi-square test.
